---
title: "Section 6.9 Zero Failure Test"
subtitle: "WeiBayes"
author: "Carles C.G."
date: "September 2, 2016"
output: html_document
---

### Substaining and reliability testing
Three tupes of Weibayes :  

- Zero failure test  
- Zero or one failure test
- Sudden Death


## Zero failure test
Given number of components in testing, failure mode (eta and beta) and the confidence of the result. 
**Basic formulas**
```{r}
 k_At_Nconf <- function(n, beta, conf){
    (-(1/n) * log(1-conf) ) ^ (1/beta) 
  }

# n Number of components at the test
# Beta of the failure mode
# conf Level of confidence fot the results
# dem_eta Characteristic life to demonstrate
time_Pass_Zero_failure  <- function(n, beta, dem_eta, conf){
  # k_At_Nconf Characteristic Life Multiplier at a confidence level
  k_At_Nconf <- function(n, beta, conf){
    (-(1/n) * log(1-conf) ) ^ (1/beta) 
  }
  
  time <- ( k_At_Nconf(n, beta, conf) * dem_eta ) %>% round(., 2)
  return( time ) 
}

time_Pass_Zero_failure(n=3, beta = 2, dem_eta = 500, conf=.9)
```


```{r libraries}
library(tidyr)
library(dplyr)
library(ggplot2)
library(plotly)
library(viridis)
theme_set(theme_bw())
```

```{r}
df <-expand.grid(
  n= c(1:10, 12, 14, 16, 18, 20, 25, 30, 40, 50),
  beta = c(seq(.5, 5, by=.5)), 
  conf=  c( 0.5, 0.6, 0.7, 0.8, 0.9, .92, .95, .97, .99))

df$k <- k_At_Nconf(n = df$n, beta = df$beta, df$conf )
df$dem_time <- time_Pass_Zero_failure(n = df$n, beta = df$beta, dem_eta = 500, df$conf) 

```
To reproduce the same table as the 6-11 change from long to wide in the 90% confidence level
```{r}
df %>% filter(conf %in% .9) %>% 
  spread(key = beta, value = k)


```



*How k (Characteristic life multiplier)  changes with beta and confidence, given a fix number (n) of components to test*

```{r}
data <-df %>% 
  mutate( facet = as.factor(n)) 
nComponents <- 2

p <- ggplot(data %>% filter(n %in% nComponents), 
            aes(x=beta, y=k, 
                group=conf, colour=conf %>% as.factor)) + 
  geom_line(size=1) +
  ggtitle(paste0("Total of ",nComponents, " testing components"))

ggplotly(p)
# + facet

```


What about a Heat map? 
```{r}
t <- df %>% as.tbl %>% 
  filter(conf %in% 0.8) %>% 
  select(beta, k, n ) %>% 
  spread(key = beta, value = k)
  
head(t)
rownames(t) <- t$n
t$n <- NULL
utils::str(t)
as.matrix(t)
m <- as.matrix(t)
m
plot_ly(z = m,  type = "heatmap") %>% 
  layout(title = "Hello", 
        xaxis = list( title = "Beta Value"), 
        yaxis = list( title = "Number of copmponents" )) 

heatmap(m)



x <- list( title = "x Axis")
y <- list( title = "LoL Axis" )
)
plot_ly(z = volcano, colorscale = "Hot", type = "heatmap") 


```
F***  Heat maps!
```{r}

```


**Seee how the characteristic life depends heavily on the number of components to test**
```{r}
q <- ggplot(data, 
            aes(x=beta, y=k, 
                group=conf, colour=conf %>% as.factor)) + 
  geom_line(size=1)  + facet_wrap(~ facet )
q
# ggplotly(q)
```


**Now change your mind to fix the confidence, and see the effect of the number of components at the chatacteristic life**
```{r}
nconf <- .9
r <- ggplot(data %>% filter(conf %in% nconf), 
            aes(x=beta, y=k, 
                group=n , colour=n)) + 
  geom_line(size=1) +
  ggtitle(paste0("Confidence of ",nconf, " in the test"))

ggplotly(r)


```



## Required sample size 