---
title: "Zero test failure"
subtitle: "Reduced testing time"
author: "Author"
date: "`r as.Date(Sys.time())`"
output: pdf_document
params: 
  dem_eta: 500
  test_eta: 200
  beta: 2
  data: NA
  confi: .5
  result: 1

---

```{r DEVELOPMENT, echo=FALSE}
# source("../investigation/bar_inputGenerator.R")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, eval = T)
```


# Result(s)

Number of components needed to test without failure to show that the failure mode was either eleminated or significantly 
improved (with a ```r params$confi * 100```% confidence).

```{r table.result, results='asis', eval=TRUE}
result <-  params$result
table.result <- data.frame("Number.of.components" = result )
t <- t(table.result)

rownames(t) <- c("Number of component(s) needed")
knitr::kable(t, caption = "Result", col.names = "Value")
```

The result(s) were calculated with the following parameters. 

```{r table, results="asis", eval=TRUE}
table.data <- data.frame(
  "dem_eta" = params$dem_eta, 
  "test_eta" = params$test_eta, 
  "confi"= params$confi)
table.data$confi <- table.data$confi*100

t <- t( table.data)
rownames(t) <- c("ETA to demonstrate", 
                 "Time/Cycles available", "Confidence level [ % ]")

knitr::kable(t, caption = "Input parameters", col.names = "Value")
```


# Reference 
- Section 6.9 Zero test failure for substaintion testing
- Formula from Table 6-3.

Number of components $$n= -( (\frac{\eta}{t})^\beta)*ln(R(t))$$

Where:  

- $\eta$ characteristics life of the failure mechanism
- $t$ time available for the zero failure test 
- $\beta$ shape of the failure mechanism
- $R(t) = 1 - Confidence$







\pagebreak

## Plot 

<br/>

  
```{r plot, fig.cap="How many componets are necessary, given a reduced testing time, to pass the test? (with  different testing time/cyle and different levels of confidence)"}
library(ggplot2)
df <- params$data

   p <- ggplot(df, 
                aes(x=components.needed, y=conf, 
                    group= test_eta, col= as.factor( test_eta))) +
      geom_line() + 
      geom_hline(aes(yintercept= params$confi)) + 
      scale_color_discrete("Time") +
      ylab("Confidence") + xlab("Number of components to test") + 
    # ggtitle(paste0("Testing Curves")) + 
      theme_minimal()
p
```

```{r, eval=FALSE}
library(plotly)
df <- params$data

p <- ggplot(df, 
            aes(x=components.needed, y=conf, 
                group= test_eta, col= as.factor( test_eta))) +
  geom_line() + 
  geom_hline(aes(yintercept= params$confi)) +
  ylab("Confidence") + xlab("Number of components to test") + 
  ggtitle(paste0("Total of ","______", " testing components")) +
  theme_gray()

ggplotly(p)
```


\pagebreak  

# Components needed: Time/Cyles vs. Confidence  

The values at the table below are fixed for the variable inputs:   

* Shape  $\beta =$ `r params$beta`
* Characteristic life $\eta =$ `r params$dem_eta`


  
```{r Table of components needed }
library(tidyr)
df <- params$data
df <- df %>% spread(key = test_eta, value = components.needed)
df <- df %>% select(-beta, -dem_eta)

knitr::kable(df)
```

Interpretation:  

  - The numeric columns are the different testing time/cycles.
  - The rows at the column *conf* are the different levels of confidence.
  - The values inside the table are the different number of components to test to meet
the requirements.
